---
title: "Gestion pesquera desde el punto  de vista empresarial"
author: "Dr. Unai Ganzedo Lopez"
date: "`r format(Sys.time(), '%d %B %Y')`"
output:
  slidy_presentation:
    footer: "Marine Support"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Diagrama de los Participante en la gestión.

```{r setup2, echo=FALSE}

suppressWarnings(suppressMessages(library(  DiagrammeR,warn.conflicts = FALSE, verbose =  F)))

grViz("
digraph dot {

graph [layout = dot]

node [shape = circle,
      style = filled,
      color = grey,
      label = '']

node [fillcolor = green]
a[label='Sostenibilidad']

node [fillcolor = orange]
b[label='Gestion Pesquera'] c[label='Clientes'] d[label='Sector Extractor']

node [fillcolor = yellow]

edge [color = grey]
a -> {b c d}
b -> {e[label='Organismos oficiales'] f[label='ONGs'] g[label='Certificación']}
c -> {k[label='Exigencia'] l[label='Disponibilidad'] m[label='Concienciación'] }
d -> {q[label='Visión de futuro'] r[label='Concienciación'] s[label='Sensibilidad']}
}")
```



## R Markdown


```{r setup1, include=FALSE}
DiagrammeR::grViz("
  digraph graph2 {
  
  graph [layout = dot, rankdir = LR]
  
  # node definitions with substituted label text
  node [shape = oval]
  a [label = '@@1']
  b [label = '@@2']
  c [label = '@@3']
  d [label = '@@4']
  
  a -> b -> c -> d
  }
  
  [1]: names(iris)[1]
  [2]: names(iris)[2]
  [3]: names(iris)[3]
  [4]: names(iris)[4]
  ", 
  height = 100)
    ```

This is an R Markdown presentation. Markdown is a simple formatting syntax for authoring HTML, PDF, and MS Word documents. For more details on using R Markdown see <http://rmarkdown.rstudio.com>.

When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document.

## Slide2 with R Output

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

